Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-24 analysis/paper/sim_survey_paper.Rmd
Draft results section of paper

A dynamic population that varies across ages, time and space is simulated with the parameter settings used here (Table \@ref(tab:par)). Figure \@ref(fig:sp) depicts the aggregate distribution of the population in one year of the simulation and the corresponding catches of one stratified random survey over this population. Layered within this, of course, is the distributions of each age, as well as age and length sampling details. Though age-specific details are not depicted for simplicity, the general pattern of spatial aggregation apparent in Figure \@ref(fig:sp) is similar across all ages. That is, all ages tend to aggregate in fairly dense clusters and low-density zones are fairly wide ranging. The survey, therefore, tends to be characterized by regions with large catches interspersed with regions of no catch (Figure \@ref(fig:sp)). The samples within each successful set are also dynamic and rarely include all age groups. This is because only moderate correlation was imposed on the distributions of ages 1-5+, allowing individuals of different ages to occupy different locations. This results in an intra-haul correlation of approximately `r sim_icc`, which, in this case, is of equal magnitude to the intra-haul correlation observed across more than 20 years of survey data of 3Ps cod.

@@

- Next discuss trend...
- Look into the ictopelagic sampling design literature (suggestion from Pierre)
- Mention that simulation is an approach widely applied to inform sampling design (program MARK, distance, RandomForest, etc.); i.e. cite the gods
- Look into work done on occupancy modeling and sampling design for such studies (i.e. book suggestion by Aaron)

@@

- Feedback and advice: Aaron Adamack, Alejandro Buren, Noel Cadigan, Karen Dwyer, Geoff Evans, Brian Healey, Paul Higdon, Danny Ings, Mariano Koen-Alonso, Joanne Morgan, Derek Osborne, Dwayne Pittman, Don Power, Martha Robertson, Mark Simpson, Brad Squires, Don Stansbury, Peter Upward
- Dave Cote for a review of a previous version of this manuscript

>>>>

A dynamic population that varies across ages, time and space was simulated with the parameter settings used here (Table \@ref(tab:par)). Figure \@ref(fig:sp) depicts the aggregate distribution of the population in one year of the simulation and the corresponding catches of one stratified random survey over this population. Layered within this, of course, is the distributions of each age, as well as age and length sampling details. Though age-specific details are not depicted for simplicity, the general pattern of spatial aggregation apparent in Figure \@ref(fig:sp) is similar across all ages. That is, all ages tend to aggregate in fairly dense clusters and low-density zones are fairly wide ranging. The survey, therefore, tends to be characterized by regions with large catches interspersed with regions of no catch (Figure \@ref(fig:sp)). The samples within each successful set are also dynamic and rarely include all age groups. This is because only moderate correlation was imposed on the distributions of ages 1-5+, allowing individuals of different ages to occupy different locations. This results in an intra-haul correlation of approximately `r sim_icc`, which, in this case, is of equal magnitude to the intra-haul correlation observed across more than 20 years of survey data of 3Ps cod.

The stratified analyses run on these simulated data provided estimates of total abundance, abundance at length and abundance at age, and different stages of sampling affect these estimates. Specifically, set density affects all estimates, length sampling affects estimates of abundance at length and abundance at age, and age sampling affects abundance at age estimates. Figure \@ref(fig:tot) depicts the consequences of different set densities on the estimates of total abundance available to the survey through the simulated series. It is clear from this figure that the probability envelopes are tighter (i.e. estimates are more precise) and bias is negligible under the higher set density scenarios ($D_{sets}$ = 0.002, and $D_{sets}$ = 0.01). Trends in total abundance appear to be slightly underestimated under the low set density scenario ($D_{sets}$ = 0.0005; Figure \@ref(fig:tot)). Likewise, abundance at length and abundance at age estimates were generally biased downward in all low set density scenarios ($D_{sets}$ = 0.0005; Figures \@ref(fig:length), \@ref(fig:age), \@ref(fig:year)). At higher set densities, abundance at length estimates are more precise and bias is less apparent (Figure \@ref(fig:length)). With the exception of a length sampling protocol of 10 measurements per set ($M_{lengths}$ = 10), there appears to be little difference in the estimates of abundance at length when the number of measurements are capped at 100 ($M_{lengths}$ = 100) or 1000 ($M_{lengths}$ = 1000; Figure \@ref(fig:length)). Some downward bias is apparent in the abundance at length estimates, especially at larger lengths, under the medium set density scenario with low length sampling effort ($D_{sets}$ = 0.002 and $M_{lengths}$ = 10; Figure \@ref(fig:length)). Upward or downward bias in abundance at age estimates is apparent in all cases except the high set density and high length sampling scenario ($D_{sets}$ = 0.01 and $M_{lengths}$ = 1000; Figure \@ref(fig:age), \@ref(fig:year)). Under both low and medium set densities ($D_{sets}$ = 0.0005 and 0.02, respectively), increasing length sampling effort from 10 or 100 measurements per set to 1000 appears to increase bias or reduce precision slightly (Figure \@ref(fig:age), \@ref(fig:year)).

For a less visual approach to assessing precision and bias, RMSE results are presented in Figures \@ref(fig:error-lines) and \@ref(fig:error-wireframe) and Table \@ref(tab:comp). Figure \@ref(fig:error-lines) depicts the effects of set density and length sampling effort on abundance at length and abundance at age estimates. In all cases, increases in set density results in large declines in RMSE (Figure \@ref(fig:error-lines)). For abundance at length estimates, RMSE declines as the number of lengths measured increases, however, gains plateau beyond a cretin point. Likewise, RMSE of abundance at age estimates decline with increased length sampling effort, but RMSE does not plateau in all set density scenarios (Figure \@ref(fig:error-lines)). While RMSE continues to decline with increased length sampling effort under the high set density scenarios ($D_{sets}$ = 0.005 to 0.01 sets / km^2^), RMSE reaches a plateau and then increases with increased length sampling effort under the medium to low set density scenarios ($D_{sets}$ = 0.002 to 0.0005 sets / km^2^; Figure \@ref(fig:error-lines)). In many cases, RMSE for both metrics is lower for scenarios with higher set density but lower length sampling effort (Figure \@ref(fig:error-lines)). Similar patterns are apparent in Figure \@ref(fig:error-wireframe) and Table \@ref(tab:comp), which focus on the consequences of set density and length and age sampling protocol on the estimates of abundance at age. Again, RMSE clearly declines with increases to set density and sometimes declines with increased length sampling effort (Figure \@ref(fig:error-wireframe)). Under both low and medium set density scenarios ($D_{sets}$ = 0.005 to 0.01 sets / km^2^), measuring a maximum of 100 fish per set appears to be better than measuring a maximum of 1000 fish per set (Figure \@ref(fig:error-wireframe); Table \@ref(tab:comp)). Decreasing the age sampling protocol below 10 ages sampled per set per length group appears to result in relatively small increases to RMSE (Figure \@ref(fig:error-wireframe); Table \@ref(tab:comp)).

@@

- Look into the ictopelagic sampling design literature (suggestion from Pierre)
- Mention that simulation is an approach widely applied to inform sampling design (program MARK, distance, RandomForest, etc.); i.e. cite the gods
- Look into work done on occupancy modeling and sampling design for such studies (i.e. book suggestion by Aaron)

@@

- Feedback and advice: Aaron Adamack, Alejandro Buren, Noel Cadigan, Karen Dwyer, Geoff Evans, Brian Healey, Paul Higdon, Danny Ings, Mariano Koen-Alonso, Joanne Morgan, Derek Osborne, Pierre Pepin, Dwayne Pittman, Don Power, Greg Robertson, Martha Robertson, Mark Simpson, Brad Squires, Don Stansbury, Peter Upward
- Dave Cote for a review of a previous version of this manuscript
